---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(tidyverse)
```

# proteins

<!-- badges: start -->
<!-- badges: end -->

This package contains the `proteins` dataset and some developmental utility functions related to proteomic and protein analyses. The dataset accompanies a workshop-style class that provides an introduction to the emerging field of Data Science in R, including data analysis and visualization, with a particular focus on its utility for biological insight.

## Installation

You **cannot** yet install the released version of tidybiology from
[CRAN](https://CRAN.R-project.org) with:

```{r eval=FALSE}
install.packages("proteins")
```

So in the meantime, use the development version from
[GitHub](https://github.com/) with:

```{r eval=FALSE}
# install.packages("devtools")
devtools::install_github("hirscheylab/proteins")
```


## Example

This is how to take a `glimpse` into the proteins dataset:

```{r}
library(proteins)
glimpse(proteins)
```
